Modeling Convective Heat Transfer Augmentation of TiO$_2$ Nanofluids using Neural Networks

### 2024-01-30 latex/paper.tex
thaghit

\documentclass{article}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{hyperref}

@@

\title{Modeling Convective Heat Transfer Augmentation of TiO$_2$ Nanofluids using Neural Networks}
\author{Zeinab pouramini}
\date{}

@@

\begin{abstract}
In this research, a neural network methodology was implemented to predict the forced convective heat transfer coefficient of nanofluids. Various solutions with distinct TiO2 nanoparticle concentrations were synthesized through the two-step method and directed upward within a vertical pipe under both laminar and turbulent flow conditions. The investigation covered diverse operational parameters, including heat flux, thermal conductivity of fluids, nanoparticle concentration, and flow Reynolds number, to quantify the convective heat transfer coefficient. These operational parameters were incorporated as inputs into an artificial neural network to model the convective heat transfer coefficient. Evaluation metrics, such as mean square error and correlation coefficient, were computed, revealing the remarkable performance of the neural network in capturing the underlying processes. The introduction of nanoparticles into the base fluid significantly amplified the forced convective heat transfer coefficient, with more pronounced effects observed in base fluids exhibiting lower thermal conductivity and flows characterized by higher Reynolds numbers and elevated heat fluxes. The findings underscore the efficacy of neural networks in elucidating the complex interactions governing convective heat transfer in nanofluids.
\end{abstract}

@@

@@

@@

Considering the wide-ranging applications of TiO2 nanofluids in energy-related technologies, this paper aims to contribute a comprehensive model for the thermal conductivity of various nanofluids. In pursuit of a model applicable to different base fluids, the thermal conductivity of the base fluid is considered as an additional input, along with size, volume fraction, and temperature. The comparative performance analysis of ANN-based models utilizes two methods, namely group method of data handling (GMDH) and multi-layer perceptron (MLP). This study proposes different models for the thermal conductivity modeling of nanofluids with TiO2 across various base fluids. Additionally, two distinct types of networks are assessed to determine the highest accuracy, while varying the architecture of the models to identify the network with the maximum reliability in forecasting the considered output.

@@

@@

\subsection{Optimization of Artificial Neural Network}

@@

@@

\begin{figure}
	\centering
	\includegraphics[width=0.8\linewidth]{fig2}
	\caption{}
	\label{fig:fig2}
\end{figure}

>>>>

\documentclass{article}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{float}
\usepackage{booktabs}

@@

\title{Modeling Convective Heat Transfer Augmentation of TiO$_2$ Nanofluids using Neural Networks}
\author{Zeinab Pouramini, Zohresadat Shahryari, Motahareh Vakili Fathabadi }
\date{}

@@

\begin{abstract}
In this research, a neural network methodology was employed to predict the forced convective heat transfer coefficient of nanofluids, considering various operational parameters such as heat flux, thermal conductivity of fluids, nanoparticle concentration, and flow Reynolds number. These parameters served as inputs for the artificial neural network, enabling the modeling of the convective heat transfer coefficient. Through the assessment of different parameter combinations, we identified the most influential factors contributing to accurate predictions. The evaluation metrics, including mean square error and correlation coefficient, demonstrated the remarkable performance of the neural network in capturing the intricate processes. The findings underscore the efficacy of neural networks in elucidating the complex interactions governing convective heat transfer in nanofluids.
\end{abstract}

@@

NNNNNNNNNNNNNNNNNNNNNNNNNNNNNNNNNNN
The introduction of nanoparticles into the base fluid significantly amplified the forced convective heat transfer coefficient, with more pronounced effects observed in base fluids exhibiting lower thermal conductivity and flows characterized by higher Reynolds numbers and elevated heat fluxes.

@@

Various solutions with distinct TiO2 nanoparticle concentrations were synthesized through the two-step method and directed upward within a vertical pipe under both laminar and turbulent flow conditions.

NNNNNNNNNNNNNNNNNNNNNNNNNNNNNNNNNNN

@@

Considering the wide-ranging applications of TiO2 nanofluids in energy-related technologies, this paper aims to contribute a comprehensive model for the thermal conductivity of various nanofluids. In pursuit of a model applicable to different base fluids, the thermal conductivity of the base fluid is considered as an additional input, along with size, volume fraction, and temperature. The comparative performance analysis of ANN-based models utilizes two methods, namely group method of data handling (GMDH) and multi-layer perceptron (MLP). This study proposes different models for the thermal conductivity modeling of nanofluids with TiO2 across various base fluids. Additionally, two distinct types of networks are assessed to determine the highest accuracy, while varying the architecture of the models to identify the network with the maximum reliability in forecasting the considered output. In Figrure \ref{fig:scatterplot}

FFFF
\begin{figure}[H]
	\centering
	\includegraphics[width=\textwidth]{pics/scatter_plot}
	\caption{This rere}
	\label{fig:scatterplot}
\end{figure}

@@

\begin{figure}[th!]
	\centering
	\includegraphics[width=0.8\linewidth]{fig2}
	\caption{}
	\label{fig:fig2}
\end{figure}

@@

\subsection{Optimization of Artificial Neural Network}
Table \ref{table:myt} shows

\begin{table}
	\centering
	\caption{This is table}
    \label{table:myt}
\begin{tabular}{c|c|c|cc|}
	\hline
	&  &  &  &  \\
	\hline
	&  &  &  &  \\
	\hline
	& kg & khjk &  &  \\

	&  &  &  &  \\
	\hline
\end{tabular}

\end{table}

@@

\begin{table}[h]
	\centering
	\begin{tabular}{lcccc}
		\toprule
		Algorithm & R2 & MSE & Function \\
		\midrule
		Back Propagation (BP) & 0.9899 & 0.0099 & trainrp \\
		Resilient Backpropagation (Rprop) & 0.9969 & 0.0031 & traincgf \\
		Fletcher–Reeves Conjugate Gradient & 0.9957 & 0.0042 & traincgp \\
		Polak–Ribière Conjugate Gradient & 0.9960 & 0.0039 & traincgb \\
		Powell–Beale Conjugate Gradient BP & 0.9990 & 0.0010 & trainlm \\
		Levenberg–Marquardt BP & 0.9944 & 0.0112 & trainscg \\
		Scaled Conjugate Gradient BP & 0.9963 & 0.0037 & trainbfg \\
		BFGS Quasi-Newton BP & 0.9957 & 0.0042 & trainoss \\
		One-Step Secant BP & 0.9910 & 0.0089 & traingd \\
		Batch Gradient Descent & 0.7778 & 0.2186 & traingdx \\
		Variable Learning Rate BP & & & \\
		\bottomrule
	\end{tabular}
	\caption{Your table caption here.}
	\label{tab:yourtablelabel}
\end{table}

@@
